Metrics

### 2023-12-11 manuscript/manuscript.tex
Add exploratory age range plot

\title[Automatic Cause of Death Assignment from Narratives with ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Narratives with ChatGPT: A Case Study of 11,000 Verbal Autopsies in Sierra Leone from 2019-2022}

@@

\author[2,3]{\fnm{Second} \sur{Author}}\email{iiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\author[1,2]{\fnm{Third} \sur{Author}}\email{iiiauthor@gmail.com}
\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Centre for Global Health Research}, \orgname{Unity Health Toronto}, \orgaddress{\street{Street}, \city{City}, \postcode{100190}, \state{State}, \country{Country}}}

\affil[2]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{10587}, \state{State}, \country{Country}}}

\affil[3]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\street{Street}, \city{City}, \postcode{610101}, \state{State}, \country{Country}}}

>>>>

\title[Automatic Cause of Death Assignment from Verbal Autopsy Narratives with ChatGPT: A Case Study of Physician Agreed Deaths in Sierra Leone from 2019-2022]{Automatic Cause of Death Assignment from Verbal Autopsy Narratives with ChatGPT: A Case Study of Physician Agreed Deaths in Sierra Leone from 2019-2022}

@@

\author[1]{\fnm{Rajeev} \sur{Kamadod}}\email{rajeevk@kentropy.com}
%\equalcont{These authors contributed equally to this work.}

\author[1]{\fnm{Cheryl} \sur{Chin}}\email{cheryl.chin@unityhealth.to}
%\equalcont{These authors contributed equally to this work.}

\author[1,3]{\fnm{Asha} \sur{Behdinan}}\email{asha.behdinan@mail.utoronto.ca}

\affil*[1]{\orgdiv{Centre for Global Health Research}, \orgname{Unity Health Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{100190}, \state{Ontario}, \country{Canada}}}

\affil[2]{\orgdiv{Dalla Lana School of Public Health}, \orgname{University of Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{10587}, \state{Ontario}, \country{Canada}}}

\affil[3]{\orgdiv{Department of Surgery}, \orgname{University of Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{610101}, \state{Ontario}, \country{Canada}}}

### 2023-12-11 src/plots.Rmd
Add exploratory age range plot

# Get counts for ages

@@

# Save the plot
asplot
ggsave("../manuscript/fig-data-agegroup.pdf", plot = asplot, dpi = 300)
```

@@

>>>>

@@

# Save the plot
asplot
ggsave("../manuscript/fig-data-agesex.pdf", plot = asplot, dpi = 300)
```

@@

Display a plot of cases by age range.

```{r, fig.height = 8, fig.width = 6}

# Format plot data
eardata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(age_range) %>%
    summarize(count = n()) %>%
    separate(
        age_range,
        into = c("age_range_value", "age_range_unit"),
        sep = " "
    ) %>%
    separate(
        age_range_value,
        into = c("age_range_min", "age_range_max"),
        sep = "-"
    ) %>%
    mutate(
        age_range_min = as.integer(age_range_min),
        age_range_max = as.integer(age_range_max),
        age_range_unit = factor(age_range_unit, levels = c(
            "Weeks",
            "Days",
            "Months",
            "Years"
        )),
        age_range_label = paste0(
            age_range_min,
            "-",
            age_range_max,
            " ",
            age_range_unit,
            "\n(n=", count, ", ", round((count / nagree) * 100), "%)"
        )
    ) %>%
    arrange(age_range_unit, age_range_min, age_range_max) %>%
    mutate(
        age_range_label = factor(age_range_label, levels = unique(age_range_label))
    )

# Plot the data
earplot <- eardata %>%
    ggplot(aes(x = age_range_label, y = count)) +
    geom_bar(
        stat = "identity",
        fill = "#1d1d1d",
        color = "white",
        width = 0.5
    ) +
    labs(
        y = y_title,
        x = element_blank()
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    ) +
    coord_flip()

# Save the plot
earplot
ggsave("../manuscript/fig-data-agerange.pdf", plot = earplot, dpi = 300)
```
